### 2014-10-30 paper/experiments.tex
adding the introduction

\subsection{Scalability}
We performed a scalability test for our system using the 3 level graph shown in Figure \ref{multigraph}. The processing data as well as the processing logic were obtained from the Grand Challenge problem of 8th ACM International conference on Distributed Event Based systems. We used the publicly available 500MB of data to generate the events.

>>>>

\subsection{Scalability}
We performed a scalability test for our system using the 3 level graph shown in Figure \ref{multigraph}. The processing data as well as the processing logic were obtained from the grand challenge problem of 8th ACM international conference on distributed event based systems. We used the publicly available 500MB of data to generate the events.
